---
title: "Looping Functions, Assignment #4"
author: "Kyle Alves"
format: 
  html: 
    code-fold: true
    embed-resources: true
    theme: solar
    toc: true
    fig-caption: true
    fig-format: png
execute:
  message: false
  warning: false
---

# Assignment 4

For this assignment you will write a new Quartro document based on the analysis of power required for different *possible_cars* from looping.RMD; You will

-   Add an additional super light car with mass 5,000 kg and a surface area 10m2

-   Compute the mean and maximum power for Cars A, B, C and for your new car, assuming that average highway speed is 80 km/hr with a standard deviation of 10km/hr; Use 2 different methods to compute the mean and maximum power for each car type; a) **FOR** loop and b) the **pmap** function from **purr**

-   Create two boxplots (one for each method (**FOR** and **pmap**)) that show the range of power consumption (across sampled speeds) for each car type.

Put the Quatro in your assignment github and submit a link on Canvas for Assignment 4 when its ready to be graded

**Grading Rubric**

1.  Correct R code for adding the super light car (5pts)
2.  Values for mean and maximum power for all 4 cars are in expected ranges (remember you are sampling so values will differ slightly) (5pts)
3.  Used both methods (**FOR** and **pmap**) correctly (4pts)
4.  Boxplots (6pts)

<!-- -->

a)  correctly show range of power consumption for each car type for the two methdos
b)  good presentation (e.g axis labels, colors)

<!-- -->

5.  Good coding practice (e.g Adequate documentation throughout) (5pts)

Total out of 25pts

```{r}
library(tidyverse)
```

```{r}
source("R/autopower.R")
# generate a structure to store info on our possible cars

#Add an additional super light car with mass 5,000 kg and a surface area 10m2
possible_cars = data.frame(name = c("A","B","C", "splt"),mass=c(10000,65000,38000, 5000), area = c(22,30,22, 10))


```

```{r}
#Compute the mean and maximum power for Cars A, B, C and for your new car, assuming that average highway speed is 80 km/hr with a standard deviation of 10km/hr; Use 2 different methods to compute the mean and maximum power for each car type; 

#make object speeds
nsample = 200
mean_speed = 80*0.277
speeds = rnorm(mean = mean_speed, sd=10*0.277, nsample)
summary(speeds)

plot(density(speeds), ylab="Distribution of Speeds in (m/s)")

```

```{r}


#a) FOR loop 
powerfor = as.data.frame(matrix(nrow = length(speeds), ncol = nrow(possible_cars)))

#checking powerfor rows and columns
nrow(possible_cars)
ncol(powerfor)

#index into matrix
for (i in 1:ncol(powerfor)) {
  powerfor[,i] =
    autopower(A=possible_cars$area[i],
              m=possible_cars$mass[i],
              V=speeds)
}

head(powerfor)

#adding column names
colnames(powerfor) = possible_cars$name

#pivot_longer for plotting
powerforlong = powerfor |>
  pivot_longer(cols = everything(),
               names_to = "car",
               values_to = "power")

#Create forloop boxplot

forloopplot = ggplot(powerforlong, aes(car, power, fill = car)) +
  geom_boxplot() +
  labs(title = "For Loop Boxplot") +
  theme_minimal()

forloopplot

```

```{r}
#Compute the mean and maximum power for Cars A, B, C and for your new car, assuming that average highway speed is 80 km/hr with a standard deviation of 10km/hr

#b) the pmap function from purr
powerpurr <- pmap(list(A=possible_cars$area, m=possible_cars$mass), autopower, V=speeds)

#add column names
powerpurr <- as.data.frame(powerfor, col.names=possible_cars$name)

#check
powerpurr

#pivot to longer rows for plotting
powerpurrlong <- powerpurr |>
  pivot_longer(cols = everything(), names_to = "car", values_to = "power")

powerpurrplot <- ggplot(powerpurrlong, aes(car, power, fill = car)) +
  geom_boxplot() +
  labs(title = "PMAP of Power Purr Function") +
  theme_minimal()

powerpurrplot
```
